Supplemental Materials for ``Universals of word order result from optimization of grammars for efficient communication''

### 2019-05-30 second-draft/pnas-word-order-si.tex
SI

Using this, we can rewrite Efficiency~(\ref{eq:efficiency}), for a given grammar $\theta$, equivalently into the parseability and predictability achieved with the best parser and language models:

@@

>>>>

Using this, we can rewrite Efficiency~(\ref{eq:efficiency-recall}), for a given grammar $\theta$, equivalently into the parseability and predictability achieved with the best parser and language models:

@@

\end{equation}\label{eq:efficiency-rewrite}
